Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-16 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:15	17:09:07	(Thu15.Oct)
la2pdf commit - 2015:10:16	07:51:03	(Fri16.Oct)

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best sidelobe suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a an multi-taper technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}. Here the best of 3 windows are selected, but unlike with LCA no micro-steered variations are used.

@@

We use LCA with variations of the Kaiser window, but a comparison to using trigonometric windows will also be provided. We extend Synnev\aa{}g's work by steering all our windows and not just some, and elaborate on the type of Kaiser windows to include and the method of steering. Then the method is applied to experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), with an operating frequency of 100\,kHz and transmit angle of 25$^\circ$.

>>>>

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best sidelobe suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a an multi-taper technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}. Here the best of 2 or 3 windows are selected, but unlike with LCA no micro-steered variations are used.

@@

We use LCA with variations of the Kaiser window, but a comparison to using trigonometric windows will also be provided. We extend Synnev\aa{}g's work by steering all our windows and not just some, and elaborate on the type of Kaiser windows to include and the method of steering. Then the method is applied to experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), with a 23$^\circ$ transmit angle operating frequency of 100\,kHz and .
